Using the internal language of toposes in algebraic geometry

### 2016-03-08 slides-pssl99.tex
Beginning of slides for PSSL 99

\title{Using the internal language of toposes in algebraic geometry}
\author{Ingo Blechschmidt}
\date{November 27th, 2015}

@@

  Topos à l'IHÉS \\
  November 27th, 2015
  \par
\end{frame}

@@

\begin{frame}[plain,c]
  \centering
  \includegraphics[scale=0.5]{images/sheafification-man}
  \sffamily

  You should totally look up:

  \hil{The Adventures of Sheafification Man}
  \par
\end{frame}

@@

  This is related (in a few cases equivalent) to the \emph{dynamical methods in
  algebra} explored by Coquand, Coste, Lombardi, Roy, and others. Their
  approach applies more generally.
  \par
\end{frame}

@@

1. Tell story; begin with MO question
2. Basics (include praise for Mike Shulman)
3. Curious field property and more advanced examples
4. Relative spectrum (also mention equivalence to Hakim's spectrum in dimension zero)
5. Outlook: synthetic algebraic geometry, relative geometry, big Zariski topos

  \scriptsize
  \begin{itemize}
    \item $\Sh(X) \models f = g$ iff~$f = g \in \F(X)$.
    \item $\Sh(X) \models f = g \vee f = h$ iff on a cover~$X = \bigcup_i U_i$,
    $f|_{U_i} = g|_{U_i}$ or~$f|_{U_i} = h|_{U_i}$.
    \item $\Sh(X) \models \neg\neg(f = g)$ iff~$f = g$ on a dense open subset
    of~$X$.
  \end{itemize}

>>>>

\title{Using the internal language of toposes in algebraic geometry}
\author{Ingo Blechschmidt}
\date{March 13th, 2016}

@@

  Special PSSL 99 \\
  in honor of Jirka Adamek's retirement \\
  March 13th, 2016
  \par
\end{frame}

@@

@@

  This is related (in a few cases equivalent) to the \emph{dynamical methods in
  algebra} explored by Coquand, Coste, Lombardi, Roy, and others. Their
  approach is more versatile.
  \par
\end{frame}

@@

1. Begin with toposes and their internal logic.
   Gauge the audience's familiarity with sheaves!

2. State the MO question by Steven Gubkin.

3. Discuss basics (include praise for Mike Shulman).

4. Explain the Diamond-translation.

5. Finish with outlook: more complex internal statements,
   synthetic algebraic geometry, relative algebraic geometry.

Do not include:
* Quasicoherence condition
* Relative spectrum
